---
title: "Assignment b4 Exercise 1"
output:
  md_document: default
  pdf_document: default
  html_document: default
---
# Introduction
- In this exercise, I analyze the word count in book 'pride pre judice'.
- I use the stopwords from stopwords package.
- Plot 2 figures, one is the wordcount including stopwords, 
  the other one is the wordcount excluding stopwords.
# Install packages
```{r}
# install.packages("janeaustenr")
# install.packages("dplyr")
# install.packages("ggplot2")
# install.packages("tidytext")
# install.packages("stopwords")
```
# Load packages
```{r}

library(janeaustenr)
library(dplyr)
library(ggplot2)
library(tidytext)
library(stopwords)
```
# Load book and apply filters to reove stopwords.
```{r}
# Load a Jane Austen book, for example "Pride and Prejudice"
text <- tibble(txt = prideprejudice)
stop_words = tibble(word = stopwords())
# Convert the text to a tidy data frame
original_text <- text %>% unnest_tokens(output = word, input = txt)
filtered_text <- original_text %>% anti_join(stop_words, by = c("word" = "word"))
```
# Count the most common words for original text (with stopwords)
```{r}
# Count the most common words
word_counts <- original_text %>%
  count(word, sort = TRUE)

# Take the top 20 most common words for plotting
top_words <- word_counts %>%
  top_n(20, n)
```
# Plot the most common words with stopwords
```{r}
# Create the plot
ggplot(top_words, aes(x = reorder(word, n), y = n, fill = word)) +
  geom_col() +
  xlab("Word") +
  ylab("Frequency") +
  geom_text(aes(label = n), nudge_y = 0.5, hjust = 0) +
  ggtitle("Top 20 Most Common Words (Including Stop Words)") +
  coord_flip()
```
# Count the most common words for original text (without stopwords)
```{r}
# Count the most common words
word_counts <- filtered_text %>%
  count(word, sort = TRUE)

# Take the top 20 most common words for plotting
top_words <- word_counts %>%
  top_n(20, n)
```
# Plot the most common words without stopwords

```{r}
# Create the plot
ggplot(top_words, aes(x = reorder(word, n), y = n, fill = word)) +
  geom_col() +
  xlab("Word") +
  ylab("Frequency") +
  geom_text(aes(label = n), nudge_y = 0.5, hjust = 0) +
  ggtitle("Top 20 Most Common Words (Excluding Stop Words)") +
  coord_flip()
```
