---
title: "Assignment b4 Exercise 2"
output:
  md_document: default
  pdf_document: default
  html_document: default
---
# Introduction
- In this exercise, I design my alex pig latin rules and implemented them in a R function.
- Also add the document and tests for the function.
- Rules
  - 1. If the first letter is not vowel, move first letter to last letter
  - 2. If the first letter is vowel, add a l*l at the front of the word, \* is the first vowel letter
  - 3. Replace all 'a' to 'u'
  - 4. Replace all 'u' to 'a'
  - 5. Add 'oy' to the end of the new word.

# Include
```{r}
library("testthat")
library("dplyr")
library("palmerpenguins")
library("usethis")
library("devtools")
```

# My function
```{r}
#' @title alex_pig_latin
#' @details
#' reveice a word and transfer it into Alex's self modified Pig Latin!
#' The rules:
#' 1. If the first letter is not vowel, move first letter to last letter
#' 2. If the first letter is vowel, add a l*l at the front of the word, \* is the first vowel letter
#' 3. Replace all 'a' to 'u'
#' 4. Replace all 'u' to 'a'
#' 5. Add 'oy' to the end of the new word.
#' @param data Input data, a word, in string format
#'
#' @return A new word performed the Alex's Pig Latin transformation!
#' @md
#' @export
#'
#' @examples
#' alex_pig_latin("happy") -> uppyhoy
#' alex_pig_latin("apple") -> luluppleoy
#' alex_pig_latin("humor") -> amorhoy
alex_pig_latin <- function(word) {
  if (!is.character(word) || !grepl("^[A-Za-z]+$", word)) {
    stop("Input must be a word string without number and symbols.")
  }
  
  if (!grepl("^[aeiouAEIOU]", word)) {
    word1 <- substring(word, 2, nchar(word))
    word <- paste0(word1, substr(word, 1, 1))
  } else {
    first_vowel <- substr(word, 1, 1)
    prefix <- paste0("l", first_vowel, "l")
    word <- paste0(prefix, word)
  }
  temp_char <- "\001"
  word <- gsub("a", temp_char, word)
  word <- gsub("u", "a", word)
  word <- gsub(temp_char, "u", word)
  word <- paste0(word, "oy")
  return(word)
}

```
# Tests
- Test the input validation and functions
```{r}
test_that("alex pig latin correctly check input word", {
  expect_error(alex_pig_latin(1), "Input must be a word string without number and symbols.")
  expect_error(alex_pig_latin(0.567), "Input must be a word string without number and symbols.")
  expect_error(alex_pig_latin("Hello!"), "Input must be a word string without number and symbols.")
  expect_error(alex_pig_latin("IronMan001"), "Input must be a word string without number and symbols.")
})

test_that("alex pig latin correctly move first letter", {
  rword <- alex_pig_latin("letter")
  expect_equal(rword, "etterloy")
  rword <- alex_pig_latin("eclipse")
  expect_equal(rword, "leleclipseoy")
})

test_that("alex pig latin correctly add letter for vowel", {
  rword <- alex_pig_latin("eclipse")
  expect_equal(rword, "leleclipseoy")
  rword <- alex_pig_latin("intrest")
  expect_equal(rword, "lilintrestoy")
})

test_that("alex pig latin correctly replace characters", {
  rword <- alex_pig_latin("apple")
  expect_equal(rword, "luluppleoy")
  rword <- alex_pig_latin("maple")
  expect_equal(rword, "uplemoy")
  rword <- alex_pig_latin("unacceptable")
  expect_equal(rword, "lalanucceptubleoy")
})


test_that("alex pig latin correctly add following 'oy'", {
  rword <- alex_pig_latin("apple")
  expect_equal(rword, "luluppleoy")
  rword <- alex_pig_latin("maple")
  expect_equal(rword, "uplemoy")
  rword <- alex_pig_latin("unacceptable")
  expect_equal(rword, "lalanucceptubleoy")
})

```
